---
title: "Data_Management_Assignment"
author: "Jana Kemp"
date: "`r Sys.Date()`"
output: html_document
---

Loading and attaching needed packages

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
```

```{r}
dung2 <- dung %>%
  select(-Ostrich, -Klipspringer)
```

Summarise dung type by vegetation type and view summaried data.
Ostrich and Klipspringer were not included as they only had one and no observations respectively and therefore cannot be plotted on a boxplot

```{r}
summary_data <- dung2 %>%
  group_by(Veg_type) %>%
  summarise(across(Bontebok:Steenbok, sum))
```

Convert data to long format to make plotting in the next step easier
```{r}
long_data <- dung2 %>%
  pivot_longer(cols = Bontebok:Steenbok, names_to = "Animal", values_to = "Count")
```

Create a pannel boxplot that shows the summarised data
```{r}
ggplot(long_data, aes(x = Veg_type, y = Count, fill = Veg_type)) +
  geom_boxplot() +
  facet_wrap(~Animal, scales = "free_y") +
  theme_minimal() +
  labs(title = "Dung Abundance by Animal and Vegetation Type",
       x = "Vegetation Type",  
       y = "Number of Dung Piles", 
       fill = "Vegetation Type")
```

